\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-28 paper.tex
finished making last-minute edits

Near the entrance of Kinkaku-ji before the ticket gate, there is a large
illustrated map. Much like the signage, there is no language on the map other
than Japanese. Using the AR camera within the app, you can project information
onto the map. Figure~\ref{fig:arMapFeature} shows the blue highlighted path of
the walking tour, including a few translated labels.

@@

When you buy a ticket to enter Kinkaku-ji, you receive a long sheet of
printed paper with calligraphy. The tickets are large and visually appealing;
they are souvenirs unto themselves that one might feel inclined to keep
around. Over the course of our three month stay we visited Kinkaku-ji
multiple times. For each visit, we received identical tickets. Seemingly, the
design on the tickets do not change on a regular basis, if at all.

Because the tickets are unlikely to change, this enables us to provide the
user with a ``virtual souvenir'' using the AR camera. This is the only AR
feature that is not tied directly to an image target that can only be
accessed at Kinkaku-ji. While the image gallery and segments of the audio
tour can be accessed at any time using the ``Chapter Select'' menu, most of
the AR features can only be experienced during the walking tour, pointing the
camera at objects physically located at the site. Augmenting the ticket
with 3D content allows visitors to take something home, giving them a reason
to launch the app later.

@@

Originally, the AR model of the Golden Pavilion was flush against the plane of
the ticket, sitting on the paper as if it were ground. Atticus suggested that
we re-orient the model such that the ticket served as a back plane. This would
allow users to hold the ticket vertically, and view the Golden Pavilion
floating in front of the ticket. This allows users to place their hands under
the base of the Golden Pavilion model as if they were holding it. Vuforia's
image tracking is flexible enough such that the image target can be partially
obscured.

\subsubsection{Early UI}
\label{sec:earlyUI}

As ideas changed and ARuko became what it is today, the UI also changed
greatly from it's early conception to the final version we used. But
that early UI would prove just as important as the final one, because
it was also how we learned many of the practices and skills we needed in order
to create the UI we settled on.

The early UI was very much a product of ARuko's development; many of it's
elements were created as new features were added. But as more features were
added, it became clear that the UI could not consist simply of buttons and 
other basic features provided by Unity. We would need to learn more about 
how to create more interesting and useful UI elements to accomodate for 
our new functionality.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{old-ui.png}
	\caption[A screenshot of our early UI]
	{A screenshot of our early UI}
	\label{fig:oldUI}
\end{figure}

Pictured in Figure~\ref{fig:oldUI} is our early UI. It was a very minimal UI,
but still covered all of the uses for our app at the time. The top of the 
screen had two dropdown menus. The one on the left, shown open, would
show AR image targets in the area that users could look for and scan. The right
dropdown would be dynamically populated in each region with buttons bearing  
different images. These images were ones that Atticus wanted to be viewable in AR using ground plane
detection. When tapped, each button would create a 3D Cube, with the given image
on each face, and place it on the ground where the user was pointing.

Learning to create these dropdown menus proved to be a very important lesson
later on, since we would put that exact knowledge to use multiple times in the
final UI. We were able to create the dynamically populated dropdown menus by 
creating an empty vertical layout group, and then using a script to create
buttons for each image based on which region the user is in, and then assign
them as children of the layout group. Then, to get the smooth open/close animation,
we used a boolean to mark the menu as open or closed and had the menu lerp to the
corresponding position each frame until it was fully open or closed.

In between these two dropdown menus is a panel that is shown empty, but in practice would
display the name for the region the user is in at the time. The empty space
in the middle of the screen is where the AR camera display would be shown. In this 
implementation, the AR functionality was the focus of the app, so it made sense
to display the AR camera feed at all times. Lastly, on the bottom is the audio slider for the audio file played in each region. 
We learned a lot about how audio sliders work in Unity with this feature, and would
expand a lot on that knowledge for the final version of the app in order to optimize
the slider's functionality and usefulness.

This early UI taught us a lot about how to make a UI in Unity. We learned a lot of 
basic things, like how all of the UI elements go on the Canvas, which represents
the phone screen, and that everything should be anchored to locations on the screen
so that they stay in the right place despite changes in screen size. 
We also learned more complicated skills that would help us a lot later. We learned
how to use audio sliders, and the ins and outs of how they work. And we learned
how to create dropdown menus that expand when opened and contract when closed, 
creating a very smooth movement affect without needing to animate the component. 
And we also learned how to create button functionality through script, allowing
for UI elements that can changed between the different tours loaded into our app.
And we would bring all of these important skills we learned into the creation
of our final UI to help make it as useful and interesting as it is now.

@@

By the end of the project, we were able to turn ARuko into an app rich with
features and polish. However, many of these features were presented to us
relatively late into the project. This section discusses some of our initial
concerns when we were first given the task of bringing Atticus' experience
design to life.

@@

One of the notable changes is the chapter select screen, which is the third
screen in Figure~\ref{fig:adobeXdDesign}. Before, we worked under the assumption
that each geolocation-triggered region would not have to be ordered in any way.
This assumption made its way into Editour, which did not currently have a way
to reorder regions once they were placed. Because of this chapter selection
screen, we needed some way to rearrange the order of regions within Editour.

The inclusion of a ``chapter selection'' screen had other notable design
implications as well. Initially different regions were triggered solely by the
GPS location. Walking into a region would prompt the available images to change
on screen. Also, a new audio track would begin to play. This forced us to
answer certain basic questions about the chapter select screen for ourselves.
For example, consider a user that steps into one region, triggering the audio
and images. Then, that user selects a chapter from the chapter selection menu,
overriding the ``true'' region the user is physically standing inside of. When
does the GPS ``take over'' again? Should the region change back to the ``true''
region once the audio of the selected region finishes? This might be intuitive
and preferred for most users, but what if the user is more interested in the
image gallery than the audio? Then, the persistence of the image gallery is
strangely tied to the duration of the audio track playing underneath. What if a
user selects a chapter, and then physically enters that region moments later?
Should the audio restart to indicate that the user has arrived at the location?
Or, will this appear as though the audio track skipped to the beginning again
for no reason? As you can imagine, this seemingly minor inclusion created a
significant amount of discussion.

@@

With more time, we might have been able to get the ground-plane image placement
feature to a state where Atticus might have liked it. We wanted to explore ways
to theme the 2D images in the 3D world, such as by framing the images in a
traditional Japanese pagoda. We had already spent two weeks on this feature, so
dropping this feature was a setback we had to plan around.

On the same screen, there is a scrollable window of text for a transcript of
the audio. Because of this, the Editour UI and tour metadata JSON file needed
to be updated to accommodate one transcript per region. On top of this, the C\#
code that interprets the tour file needed to be updated to expect an audio
transcript field.  Figure~\ref{fig:editourAdditions} shows the UI elements that
changed in order to add these new features. The arrows next to the region name
can be used to move the ``Region Card'' up and down in the side bar. In the
``Media'' tab, there is also a text area to include a transcript of the
uploaded audio file.

@@

At this point, the codebase for Editour was already around three thousand lines
of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules,
the only external library we used for Editour was Leaflet, an open-source
JavaScript library for interactive maps~\autocite{leafletjs}. We did not use
any libraries for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel.
This was likely an appropriate decision for a JavaScript project of this scope.
Considering we had limited to no experience with React or Angular, it was also
faster to develop the UI in the way we were used to from previous experience.
But if we were to continue to develop Editour, UI libraries and frontend build
tools would be something to consider. With these changing requirements, the
Editour was becoming onerous to maintain at this stage of the project. Luckily,
these changes were still manageable to implement.

@@

%TODO should this paragraph move somewhere else?
Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
target capabilities for scanning objects outside of the expected use case, such
as 3D landscapes or the side of a building. We had serious doubts about how
well this would work, and our suspicions were confirmed after some field
testing. This was the reasoning behind focusing on ground-plane detection
instead of image targets; ground-plane detection can be used anywhere, and is
much more reliable than treating 3D objects as 2D image targets.

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI
elements as PNGs, such as the buttons to enter AR mode and view the map. We
briefly explored a few solutions to automating the task of getting the Adobe XD
project into Unity. We found one payed extension (for \$18) on the Unity Asset
store called ``Experience Importer - Adobe Xd files importer.'' The download
page for this extension claims ``Transfer AdobeXd project directly to Unity.
Forget about hours of positioning objects. They're already there! Just drag .xd
file to project and...  voila!''~\autocite{glasseye2019}.  We suspect this
sounds too good to be true because it is. As of September
20\textsuperscript{th}, 2019, there are 6 user reviews. All of the five-star
reviews were have the caveat ``Reviewer was gifted package by publisher'' which
which we interpreted as a warning sign. Because of this, we decided to rebuild
the UI largely from the ground up, using the Adobe XD file to guide us.
%TODO refer to the section that discusses building the ui

@@

While the newly proposed UI by Atticus was certainly a huge step up from
our previous one, the things we had learned the first time around helped
a lot in overcoming this rather large request in the relatively short amount
of time we had. We had to get much more creative with how we implemented the
UI and how everything worked together, but in the end this allowed us to 
create a rather impressive final UI for and app that we're proud of.

One of the first major challenges we had to tackle was the need to switch
modes while keeping certain UI elements constant. So when a user goes from
the home screen to the Route Map, or into AR Mode, we needed the mode buttons,
audio components, and region info to remain. We went did this by splitting up
screen space into panels, with one for the region info up top, one each for the
mode buttons and audio components on the bottom, and one for the different 
modes in the middle of the screen. Then, within the mode panel, each mode 
screen would be assigned as children, and toggled active or inactive based on 
which mode the user is in at the time. That way, on-screen content can change
while important UI elements remain constant.

Now, within the mode problem itself, there were other important things to 
consider. One such topic was how to handle AR Mode. Previously, we had just
left the AR camera running at all times, since it was the primary feature of 
the app. But now, the focus was much more on the images and audio transcription
in each region. For this, we found that we were able to disable and re-enable
the AR camera in script, so we could turn it off while other modes were the
focus, and back on when needed. We also weren't sure at first what to do about
the chapter select menu, as it was also content that would occupy the space of
the mode panel on screen, but needed to be accessible anywhere via the top 
panel. Using our experience creating dropdown menus in the early UI, we simply
left the chapter select menu enabled at all times, and lerped it open or closed
as needed.

Another group of challenges were created by the content of the main screen,
which showed the images and audio transcript associated with each region. To 
display the images, we wanted the user to be able to click through them like
an image gallery, but weren't sure how to do so in a way that was smooth and
looked nice. But once again, our experience with dropdown menus came in handy. 
We created the gallery out of a horizontal layout group, populated it with 
images dynamically in each region, and then had the buttons lerp the gallery
to different positions in order to switch between each image in a smooth and 
pleasing way. As for the audio transcript, we knew we needed a scrollable
text field that could accomodate varying amounts of text, since the audio files
varied so greatly in length. After doing some research, we found a way to use 
a vertical layout group to create a text field that expanded vertically, within
a predefined bounds, to fit any amount of text provided to it.

At first, our route map screen was rather simple. It was just a static image
of the map, with the route drawn on it, that the user could scroll up and down,
since the image was too tall for the screen. But because the map was so zoomed
out, certain features and text on the map were hard to see. This could also 
make it hard to tell where someone is on the route. So we needed a way to zoom
in on the map and scroll around it, even though Unity doesn't provide this 
relatively common functionality in a standard way. After doing some research, 
were able to write a script that used some of Unity's Input library to get
touch input and use it to zoom in and out on the map within a predefined 
bounds.

The last major UI implementation obstacle we had to overcome was a way to keep
audio playing with the phone in your pocket. Atticus insisted that this sort of
feature was required so that users could listen to the audio tour without using
any of the other functionality the app provides, like the image gallery in each
region or the AR features. But despite how common it is for apps to play audio 
in the background or while the phone is locked , Unity does not provide a way 
to accomplish this either. The way we got around this was by figuring out a way
to prevent UI elements from accidentally being triggered while the phone is 
still unlocked and in the app in the user's pocket. We added a mode to the mode
panel that consists of simply a high opacity black screen with a slider on it,
and added a button to the chapter select dropdown in order to trigger this 
mode. What this pocket mode does is that, because of where it is placed in the 
Unity hierarchy, when it is enabled, it blocks input to all other active UI
components. Then the slider works much like the slider on old Apple devices,
where you slide it from one end to the other to "unlock" the app again, 
re-enabling UI interaction. We figured that it would be rather difficult to 
accidentally trigger the slider while the phone is in one's pocket, and even
have the slider reset if it is only slided partially before letting go.

The rest of the final UI consisted primarily of standard UI features, like 
different basic buttons and panels in different places throughout the app. 
We were ultimately able to replicate Atticus's Adobe XD file almost 
perfectly, allowing us to use a great UI for this app we've worked so hard on.

@@

Both pieces of our project---the Editour and ARuko---are designed to be used by
people who aren't programmers. The Editour will be used by Atticus in the future
to design more tours, and ARuko will be used by the general public. Because of
this, we needed to do extensive testing to ensure not only that the products
work as intended without bugs, but also that they would be pleasant and easy to
use for their intended users.

@@

Because the Editour is intended only to be a tool to aid Atticus in creating
tours our user testing was less rigid. Even so, the frontend and backend we
built for Editour ended up being largely reliable. The reliability issues
stemmed from the hosting provider, which was out of our control.

@@

For each of the six API endpoints that the backend responds to we wrote an
extensive series of end-to-end tests to ensure that each step along the pipeline
from receiving a request to sending a response worked properly. We also wrote
many fuzz tests, to make sure the backend would respond correctly to invalid
requests, e.g. by responding with an HTTP 400 error message~\autocite{rfc7231}.

@@

We suspect that Editour might have a life outside of this particular use case
for designing tours, depending on how we choose to further develop this
software. This is why Editour is perhaps more polished than your typical tool
purely for internal use.

For the duration of the project however, Editour only had to be used by us
three and Atticus. Therefore, the testing for the frontend of Editour was less
systematic than other parts of the software stack. This decision also helped us
focus our efforts on testing the reliability and user experience of ARuko. That
being said, we were able to add many feature and get the Editour experience to
a polished state through our own testing, using GitHub's tools to keep us
organized.

In order to test for bugs, all three of us periodically interacted with
successive builds of the frontend. When bugs were found, we would log these as
``Issues'' on the GitHub repository. These issues would get resolved in
successive pull requests.

@@

Issues and feature requests alike got resolved in future pull requests. We
resolved over thirty issues and feature requests using this workflow. The
GitHub issues tab (which can be see in Figure~\ref{fig:issuesPageExample}) was
very useful for making sure we made use of our user testing and bug testing.

@@

The UI and AR features of the app are very important to the user experience. At
the same time, ARuko is not as purely graphical as it may seem. There is a
significant amount of ``business logic'' that interprets the tour from the
Editour file. On top of this, the geometric checks to test whether the user is
inside a particular arbitrarily-defined geographic region are very important to
get right.  Using Unity's built-in NUnit unit testing framework, we wrote tests
to verify whether the tour data was being parsed correctly, and whether the tour
would be run correctly.

As a reminder, regions that trigger audio can be a set of three or more points
that define a closed polygon. Using the user's GPS location, the app needs to
periodically run a check to see if the user is located within one of those
polygons, which can be either concave or convex.

One decent algorithm for accomplishing this is by drawing a ray from a given
point to infinity. Barring edge cases (which will be discussed shortly) the
point is inside the polygon if the ray passes through an even number of line
segments.  The point is outside of the polygon if the ray intersects an odd
number of times. Figure~\ref{fig:intersectionsDiagram} does not serve as a
proof, but should at least make it clear why this works. This algorithm's time
complexity is $O(n)$, where $n$ is the sum total of the number of vertices of
all of the polygons being tested~\autocite{geeksforgeekspolygon}.

@@

For this, we implemented a few mathematical functions for individual parts of
the algorithm, such as testing for intersection. We wrote unit tests to test
each part of the algorithm, so we could be confident that the GPS component of
the app would correctly place users into the correct regions.

There is one edge case where this algorithm has difficulties. If the ray that
is drawn for testing intersections passes directly through a vertex, the
algorithm will count two intersections instead of just one. Even though this is
highly unlikely considering our use case, we decided that our algorithm should
be robust enough to handle this on a matter of principle. Unit-testing helped us
catch and deal with this edge case.

@@

Because it was not feasible to travel to Kinkaku-ji every time we needed to
test the GPS functionality of the app, we used Editour to design an example
tour around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed
us to catch various bugs before we created a finalized prototype for
field-testing at Kinkaku-ji. The tour represented in \ref{fig:ritsuTour} is
what we used for testing the app. The ``C-Shaped Region'' helped us test
concave regions. This uniquely shaped region also prompted us to think about
what UI behavior made the most sense if a user were to walk into a region, walk
out and then in again. We decided that it was awkward if the audio restarted
upon re-entering a region, since the audio would still be playing once a user
left the region. (The region at the bottom surrounding our dormitories was added
for our convenience, allowing us to test the app while we were away from the
lab.) As we began to implement more complex UI that changed based on GPS
position in various ways, directly taking the tour by walking around was an
invaluable way to test. Section~\ref{sec:adobeXdDesign} details how the UI grew
in complexity in the late stages of the project. Having a way to regularly run
field tests was integral to polishing the app in time before we revisited
Kinkaku-ji.  Because the Editour was flexible enough to easily swap out media
and add regions to the tour, the Editour proved itself to be as helpful for
testing as it was for crafting the final tour that could be taken at
Kinkaku-ji.

If we were ever feeling too tired to test the app by walking around, we also
mocked the GPS coordinates in software. This allowed us to simulate walking in
a single direction without actually having to move or build to a mobile device.

@@

Our first day of on-site testing with the app took place on September
6\textsuperscript{th}. Using Editour, we rebuilt the izi.TRAVEL audio tour that
Atticus already created. The first version of the rebuilt tour had regions that
were relatively small; some regions were only a few meters across. This version
of the tour can be seen in Figure~\ref{fig:kinkakujiTour}. This day of testing
prior to the redesign discussed in Section~\ref{sec:adobeXdDesign}.

@@

Due to concerns about GPS accuracy, we adapted the tour-file \texttt{kinkakuji}
to create a second, ``chunkier'' tour.  In the tour-file
\texttt{kinkakuji-chunkier}, we expanded all of the regions to accommodate for
potential GPS inaccuracies that could place the user outside the range of the
audio-trigger region.  Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour
that we used for field testing at Kinkaku-ji.

@@

We tested using two phones at the same time: an iPhone 8 and a Samsung Galaxy
S7. The iPhone 8 is newer, more powerful and therefore more suited for use with
AR. We primarily used this phone to test the AR features of the app. Even
though the Samsung Galaxy had difficulty with basic AR features such as
ground-plane detection, it was still capable of triggering the audio track
based on GPS position.

>>>>

Near the entrance of Kinkaku-ji before the ticket gate, there is a large
illustrated map. Much like the signage, there is no language on the map other
than Japanese. Using the AR camera within the app, information can be projected
onto the map. Figure~\ref{fig:arMapFeature} shows the blue highlighted path of
the walking tour, including a few translated labels.

@@

Tickets to enter Kinkaku-ji are long sheets of printed paper with calligraphy.
The tickets are large and visually appealing; they are souvenirs unto themselves
that one might feel inclined to keep around. Over the course of our three month
stay we visited Kinkaku-ji multiple times. For each visit, we received identical
tickets. Seemingly, the design on the tickets do not change on a regular basis,
if at all.

Because the tickets are unlikely to change frequently, this enables us to
provide the user with a ``virtual souvenir'' using the AR camera. This is the
only AR feature that is not tied directly to an image target that can only be
accessed at Kinkaku-ji. While the image gallery and segments of the audio tour
can be accessed at any time using the ``Chapter Select'' menu, most of the AR
features can only be experienced during the walking tour, pointing the camera at
objects physically located at the site. Augmenting the ticket with 3D content
allows visitors to take something home, giving them a reason to launch the app
later.

@@

Originally, the AR model of the Golden Pavilion was flush against the plane of
the ticket, sitting on the paper as if it were ground. Atticus suggested that we
re-orient the model such that the ticket served as a back plane. This would
allow users to hold the ticket vertically, and view the Golden Pavilion floating
in front of the ticket. This allows users to place their hands under the base of
the Golden Pavilion model as if they were holding it; Vuforia's image tracking
is flexible enough such that the image target can be partially obscured by the
hand.

\subsubsection{Early User Interface}
\label{sec:earlyUserInterface}

As ideas changed and ARuko became what it is today, the user interface (UI) also
changed greatly from its early conception to the final version. Still, the early
UI was a valuable learning experience, providing us with skills that were useful
when building the final version.

The early UI was very much a product of ARuko's development; many of its
elements were created on the fly as new features were added. As more features
were added, it became clear that the UI could not consist simply of buttons and
other basic features provided by Unity. We would need to learn more about how to
create more interesting and useful UI elements to accommodate for our new
functionality.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{old-ui.png}
	\caption{A screenshot of our early UI}
	\label{fig:oldUI}
\end{figure}

Pictured in Figure~\ref{fig:oldUI} is our early UI. It was a very minimal UI,
but still covered all of the uses for our app at the time. The top of the screen
had two dropdown menus. The one on the left (which is open shown open in
Figure~\ref{fig:oldUI}) shows AR image targets in the area that users could
look for and scan. The right dropdown would be dynamically populated in each
region with buttons bearing different images. These images were ones that
Atticus wanted to be viewable in AR using ground plane detection. When tapped,
each button would create a 3D Cube, with the given image on each face, and place
it on the ground where the user was pointing. 
%TODO provide a figure of the AR cube

Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
target capabilities for scanning objects outside of the expected use case, such
as 3D landscapes or the side of a building. We had serious doubts about how
well this would work, and our suspicions were confirmed after some field
testing. This was the reasoning behind focusing on ground-plane detection
instead of image targets; ground-plane detection can be used anywhere, and is
much more reliable than treating 3D objects as 2D image targets.

Learning to create these dropdown menus proved to be a very important lesson
later on, since we would put that exact knowledge to use multiple times in the
final UI. We were able to create the dynamically populated dropdown menus by
creating an empty vertical layout group. Then, a script would create buttons for
each image to display, and assign those images as children of the layout group.
Then, to get the smooth open/close animation, we ``lerp'' (linearly interpolate)
the menu to the corresponding position each frame until it is fully open or
closed. In between these two dropdown menus is a panel that would display the
name for the region the user is in at the time. The empty space in the middle of
the screen is where the AR camera display would be shown. In this
implementation, the AR functionality was the focus of the app, so it made sense
to display the AR camera feed at all times. Lastly, on the bottom is the audio
slider for the audio file played in each region. We learned about how audio
sliders work in Unity with this feature, and would expand on that knowledge for
the final version of the app in order to optimize the slider's functionality.

Although most elements of the initial UI did not survive into the final product,
it was still quite valuable as a learning tool. While crafting this prototype we
discovered many of the intricacies of UI design in Unity. For example, all UI
elements must be attached to a Unity canvas element, which covers the entire
phone screen. Elements should be anchored to edges or corners of this canvas so
that they stay in a constant location on different-size screens.

@@

By the end of the project, we were able to turn ARuko into an app rich with
features and polish. However, many of these features were requested relatively
late into the project. This section discusses some of our initial concerns when
we were first given the task of bringing Atticus's ideas to life.

@@

One of the notable changes is the chapter select screen, which is the third
screen in Figure~\ref{fig:adobeXdDesign}. Before, we worked under the assumption
that each geolocation-triggered region would not have to be ordered in any way.
This assumption made its way into Editour, which at the time did not have a way
to reorder regions once they were placed. Because of this chapter selection
screen, we needed some way to specify and rearrange the order of regions within
Editour.

The inclusion of a ``chapter selection'' screen had other notable design
implications as well. Initially different regions were triggered solely by the
GPS location. Walking into a region would cause the available images to change
on screen. Also, a new audio track would begin to play. This forced us to answer
certain basic questions about the chapter select screen for ourselves. For
example, consider a user that steps into one region, triggering the audio and
images. Then, that user selects a chapter from the chapter selection menu,
overriding the ``true'' region the user is physically standing inside of. When
does the GPS ``take over'' again? Should the region change back to the ``true''
region once the audio of the selected region finishes? This might be intuitive
and preferred for most users, but what if the user is more interested in the
image gallery than the audio? Then, the persistence of the image gallery is
strangely tied to the duration of the audio track playing underneath. What if a
user selects a chapter, and then physically enters that region moments later?
Should the audio restart to indicate that the user has arrived at the location,
or will this appear as though the audio track skipped to the beginning again for
no reason? This seemingly minor inclusion created a significant amount of
discussion.

@@

With more time, we might have been able to get the ground-plane image placement
feature to a state where Atticus might have liked it. We wanted to explore ways
to theme the 2D images in the 3D world, such as by framing the images in a
traditional Japanese pagoda. We had already spent two weeks on this feature, so
dropping it was a setback we had to plan around.

On the same screen, there is a scrollable window of text for a transcript of
the audio. Because of this, the Editour UI and tour metadata JSON file needed
to be updated to accommodate one transcript per region. On top of this, the C\#
code that interprets the tour file needed to be updated to expect an audio
transcript field.  Figure~\ref{fig:editourAdditions} shows the UI elements that
changed in order to add these new features.

@@

At this point, the codebase for Editour was already around three thousand lines
of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules, the
only external library we used for Editour was Leaflet, an open-source JavaScript
library for interactive maps~\autocite{leafletjs}. We did not use any framework
for developing frontends like Facebook's React or Google's Angular. Instead, all
of the complex UI interactions were handled by modifying the DOM directly with
JavaScript's built-in functionality. Furthermore, we did not use any advanced
frontend build tools such as Rollup, webpack or Parcel. For a JavaScript project
of this scope, this was the correct decision. Considering we had limited
knowledge of React or Angular, it was also faster to develop the UI in the
way we were used to from previous experience. But if we were to continue to
develop Editour, UI libraries and frontend build tools would be something to
consider. With these changing requirements, the Editour was becoming onerous to
maintain at this stage of the project. Luckily, these changes were still
manageable to implement.

@@

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI
elements as PNGs, such as the buttons to enter AR mode and view the map. We
briefly explored a few solutions to automating the task of getting the Adobe XD
project into Unity. We found one paid extension (for \$18) on the Unity Asset
store called ``Experience Importer - Adobe Xd files importer.'' The download
page for this extension claims ``Transfer AdobeXd project directly to Unity.
Forget about hours of positioning objects. They're already there! Just drag .xd
file to project and...  voila!''~\autocite{glasseye2019}.  We suspect this
sounds too good to be true because it is. As of September
20\textsuperscript{th}, 2019, there are 6 user reviews. All of the five-star
reviews were have the caveat ``Reviewer was gifted package by publisher'' which
which we interpreted as a warning sign. Because of this, we decided to rebuild
the UI largely from the ground up, using the Adobe XD file to guide us.
%TODO refer to the section that discusses building the ui

@@

The lessons we learned from the initial UI design (see
Section~\ref{sec:earlyUserInterface}) helped us create the final design in such
a short period of time. Although the new UI is significantly more complicated
than the original prototype, we were able to implement all of Atticus's desired
features within the time limit.

One of the first hurdles we had to overcome was keeping certain UI elements
constant while the user switches between the home screen, AR camera, and map
view. The mode buttons, audio controls, and top bar need to remain on the screen
at all times. To achieve this, we divided the screen into panels. Only one of
the three main panels are set to ``active'' at a given time. Previously, the app
left the AR camera running at all times, since there was only one main screen.
In the new design, the AR camera is only set to ``active'' only when the AR
panel is being shown. This prevents us from incurring unnecessary computational
cost when the AR camera was not in use.

Another group of challenges were created by the content of the main screen,
which showed the images and audio transcript associated with each region. To 
display the images, we wanted the user to be able to click through them like
an image gallery.

We created the gallery out of a horizontal layout group, populated it with
images dynamically in each region, and then had the buttons ``lerp'' the gallery
to different positions in order to switch between each image in a smooth and
pleasing way. As for the audio transcript, we knew we needed a scrollable text
field that could accomodate varying amounts of text, since the audio files
varied so greatly in length. We created a vertical layout group to create a text
field that expanded vertically within predefined bounds to fit an arbitrary
amount of text.

The last major UI implementation obstacle we had to overcome was a way to keep
audio playing with the phone in your pocket. Atticus insisted that this sort of
feature was required so that users could listen to the audio tour without using
any of the other functionality the app provides, like the image gallery in each
region or the AR features. Despite how common it is for apps to play audio in
the background or while the phone is locked, Unity does not provide a way to
accomplish this. Our workaround was to create a ``pocket mode'' that prevents UI
elements from accidentally being triggered. The user exits pocket mode with a
deliberate swipe to the right. If the slider is released partway through the
action, the slider springs back to the beginning. We were ultimately able to
replicate Atticus's Adobe XD file almost perfectly.

@@

Both pieces of our project---Editour and ARuko---are designed to be used by
people who are not programmers. Editour will be used by Atticus in the future to
design more tours, and ARuko will be used by the general public. Because of
this, we needed to do extensive testing to ensure not only that the products
work as intended without bugs, but also that they would be pleasant and easy to
use for their intended users.

@@

Because Editour is simply an internal tool, our user testing was less rigid.
Even so, the frontend and backend we built for Editour ended up being reliable.
The few reliability issues stemmed from the hosting provider, which was out of
our control.

@@

For each of the six API endpoints that the backend responds to, we wrote an
extensive series of end-to-end tests to ensure that each step along the pipeline
from receiving a request to sending a response worked properly. We also wrote
many fuzz tests to make sure the backend would respond correctly to invalid
requests, for example, by responding with an HTTP 400 error
message~\autocite{rfc7231}.

@@

We suspect that Editour might have a life outside of this particular use case
depending on how it is developed later on. This is why Editour is perhaps more
polished than your typical tool purely for internal use.

For the duration of the project however, Editour only had to be used our team
and Atticus. Therefore, the testing for the frontend of Editour was less
systematic than other parts of the software stack. This decision also helped us
focus our efforts on testing the reliability and user experience of ARuko.
Still, we were able to add many features and get the Editour experience to a
polished state through our own testing, using GitHub's tools to keep us
organized.

In order to test for bugs, all three of us periodically interacted with
successive builds of the frontend. When bugs were found, we would log these as
``Issues'' on the GitHub repository.

@@

Issues and feature requests alike got resolved in future pull requests. We
resolved over thirty issues and feature requests using this workflow. The GitHub
issues tab (which can be see in Figure~\ref{fig:issuesPageExample}) was very
useful for ensuring we made use of our user testing and bug testing.

@@

The UI and AR features of the app are very important to the user experience. At
the same time, ARuko is not as purely graphical as it may seem. There is a
significant amount of ``business logic'' that interprets the tour from the
Editour file. On top of this, the geometric tests to check whether the user is
inside a particular arbitrarily-defined geographic region are very important to
get right.  Using Unity's built-in NUnit unit testing framework, we wrote tests
to verify whether the tour data was being parsed correctly, and whether the tour
would be run correctly.

Regions are a set of three or more points that define a closed polygon. Using
the user's GPS location, the app needs to periodically run a check to see if the
user is located within one of those polygons.

% TODO move the stuff about the algorithm into the implementation section
One decent algorithm for accomplishing this is by drawing a ray from a given
point to infinity. Barring edge cases (which will be discussed shortly) the
point is inside the polygon if the ray passes through an even number of line
segments.  The point is outside of the polygon if the ray intersects an odd
number of times. Figure~\ref{fig:intersectionsDiagram} does not serve as a
proof, but should at least make it clear why this works. This algorithm's time
complexity is $O(n)$, where $n$ is the sum total of the number of vertices of
all of the polygons being tested~\autocite{geeksforgeekspolygon}.

@@

For this, we implemented a few mathematical functions for individual parts of
the algorithm, such as one that tests to see if two lines intersect. We wrote
unit tests to verify each part of the algorithm. This gave us confidence that
the GPS component of the app would place users into the correct regions.

There is one edge case where this algorithm has difficulties. If the ray that is
drawn for testing intersections passes directly through a vertex, the algorithm
will count two intersections instead of just one. Even though this is highly
unlikely considering our use case, we decided that our algorithm should be
robust enough to handle this on a matter of principle. We solved this by running
a check on all vertices in the polygon to see if any were exactly colinear with
the ray. If this is the case, one intersection count is subtracted from the
total. Unit testing helped us catch and deal with this edge case.

@@

Because it was not feasible to travel to Kinkaku-ji every time we needed to test
the GPS functionality of the app, we used Editour to design an example tour
around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed us to
catch various bugs before we created a finalized prototype for field-testing at
Kinkaku-ji. The tour represented in Figure~\ref{fig:ritsuTour} is what we used
for testing the app. The ``C-Shaped Region'' helped us test concave regions.
This uniquely shaped region also prompted us to think about what UI behavior
made the most sense if a user were to walk into a region, walk out and then in
again. We decided that it was awkward if the audio restarted upon re-entering a
region, since the audio would still be playing once a user left the region. As
we began to implement more complex UI that changed based on GPS position in
various ways, directly taking the tour by walking around was an invaluable way
to test. Section~\ref{sec:adobeXdDesign} details how the UI grew in complexity
in the late stages of the project. Having a way to regularly run field tests was
integral to polishing the app in time before we revisited Kinkaku-ji.  Because
the Editour was flexible enough to easily swap out media and add regions to the
tour, the Editour proved itself to be as helpful for testing as it was for
crafting the final tour that could be taken at Kinkaku-ji.

If we were ever feeling too tired to test the app by walking around, we also
mocked the GPS coordinates in software. This allowed us to simulate walking in a
single direction without actually having to build to a mobile device or move.

@@

Our first day of on-site testing with the app took place on September
6\textsuperscript{th}. Using Editour, we rebuilt the izi.TRAVEL audio tour that
Atticus had created previously. The first version of the reimplemented tour had
regions that were relatively small; some regions were only a few meters across.
This version of the tour can be seen in Figure~\ref{fig:kinkakujiTour}. On this
day of testing, we still had the limited UI described in
Section~\ref{sec:earlyUserInterface}.

@@

Due to concerns about GPS accuracy, we adapted the tour-file \texttt{kinkakuji}
to create a second, ``chunkier'' tour.  In the tour-file
\texttt{kinkakuji-chunkier}, we expanded all of the regions to accommodate for
potential GPS inaccuracies that could place the user outside the range of the
region.  Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour that we used
for field testing at Kinkaku-ji.

@@

We tested using two phones at the same time: an iPhone 8 and a Samsung Galaxy
S7. The iPhone 8 is newer, more powerful and therefore more suited for use with
AR. We primarily used this phone to test the AR features of the app. Even
though the Galaxy S7 had difficulty with basic AR features such as
ground-plane detection, it was still capable of triggering the audio track
based on GPS position.

As discussed in Section~\ref{sec:testingARuko}, our previous testing involved
creating a ``mock tour'' on the Ritsumeikan campus. While this let us know
generally which features of the app were working, it was very difficult to know
how ahead of time how well our app would work on-site.
